### 2013-09-17 manuscripts/reply/reply.tex
Fleshing out reply intro.

        \MakeUppercase{\large\bfseries Title}

        \vspace{12pt}
        \textbf{Running head:} \MakeUppercase{Running head}

@@

\newpage
\noindent Both papers are largely in agreement.
In fact, \citet{Hickerson2013} reiterate a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main differences in their perspectives are centered around
(1) the means by which broad uniform priors cause the poor behavior of \msb,
and
(2) how to potentially ameliorate this issue.

\citet{Oaks2012} conclude the primary mechanism by which broad priors cause the
poor behavior of the method is likely the low marginal likelihoods of
parameter-rich models integrated over vast parameter space with low probability
of producing the data, yet relatively high prior density \citep[this is often
referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of the method could be sound.
\citet{Hickerson2013} take a more pessimistic view of the bias, and suggest the
bias is intrinsic to \msb, i.e., the method's rejection algorithm is
inefficient and will be increasingly biased as the overall space of the model
increases, either as a function of the number of taxon pairs or the width of
the uniform priors on nuisance parameters.

>>>>

        \MakeUppercase{\large\bfseries Why you should not fix a biased
        model-choice method by adding an additional dimension of model choice:
        A reply to Hickerson et al.}

        \vspace{12pt}
        \textbf{Running head:} \MakeUppercase{Approximate Bayesian model
        choice}

@@

\newpage
\noindent Recently, this journal has served as a venue for discussion of the
potential pitfalls of approximate Bayesian methods of comparative
phylogeographical model choice.
\citet{Oaks2012} published their findings that the method \msb can often be
biased towards inferring models of temporally clustered divergence times
among taxon pairs.
\citet{Hickerson2013} has published a response to this paper where they
present a model-averaging approach that they conclude circumvents the poor
behavior of the method revealved by \citet{Oaks2012}.
Both of these papers are largely in agreement.
In fact, \citet{Hickerson2013} reiterate a lot of the discussion of
\citet{Oaks2012} regarding the impact of broad uniform priors on Bayesian model
choice.
The main differences in their perspectives are centered around
(1) the means by which broad uniform priors cause the poor behavior of \msb,
and
(2) how to potentially ameliorate this issue.

\citet{Oaks2012} conclude the primary mechanism by which broad priors cause the
poor behavior of the method is likely the low marginal likelihoods of
parameter-rich models integrated over vast parameter space with low probability
of producing the data, yet relatively high prior density \citep[this is often
referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of the method could be sound.
\citet{Hickerson2013} take a more pessimistic view of the bias, and suggest it
is intrinsic to \msb, i.e., the method's rejection algorithm is
inefficient and will be increasingly biased as the overall space of the model
increases, either as a function of the number of taxon pairs or the width of
the uniform priors on nuisance parameters.
They support their position by giving a probabilistic argument that focuses on
only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on dubious assumptions, and does not
explain the bias of the method found in several analyses of \citet{Oaks2012}.
We reiterate several of the findings of \citet{Oaks2012} as well as present
results of additional analyses, which strongly suggest that Lindley's paradox
is playing a larger role in the poor behavior of the method.

\citet{Oaks2012} suggest that more cogent prior probability distributions on
divergence models and nuisance parameters could mitigate the effect of
Lindley's paradox.
They also layout a set of simulation-based procedures for determining power,
accuracy, and robustness of the method given a dataset, and recommend any
application of \msb should be accompanied by such procedures, especially
if any biological conclusions are going to drawn from the results.
\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
for accommodating uncertainty in prior selection, and champion the method
as a means of avoiding the pitfalls raised by \citet{Oaks2012}.
Unfortunately, we show that fundamental errors in this approach render some of
their results invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s \citeyear{Hickerson2013}
approach.
Our results demonstrate that the method is biased and dangerous.
The approach merely provides another means by which the model can ``escape''
large parameter space, and the bias towards models with smaller space still
remaines.
